---
title: "Eating Out"
author: "Jaelynn Schultz"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
  
Based on the above data, we can see that roughly 960 white people eat out, while 200 white people opt to stay home. As for black people, 200 decide to eat out while 100 stay in. As for the other races, around 100 people will eat out while 50 stay in. Percentage wise, this would mean roughly 80% of white people eat out while the rest stay in, and about 70% of black people and other races go out and 20% stay in.  


```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```
  
Based on the numerical summaries with the accurate numerical data, we can see that 83.13% of white people eat out while 16.87% stay in, 69.19% of black people eat out and 30.81% stay in, and 72.12% of all other races eat out while 27.88% stay in. This shows that black people and other races are slightly less likely to eat out in comparison to white people. Black people and other races show similar rates of eating out. Additionally, the table above shows that white people where among the majority who stated they eat out. Out of all the people that said yes to eating out, 81.69% were white, 11.83% were black, and 6.48% were of another race. 


